### 2015-08-13 doc/thesis/evaluation.tex
Improving table formats

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
\textbf{Case study} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
Lua Standard Library & 64\% & 5\% & 8\% & 23\% & 129 \\ % 100%
\hline
MD5 & 100\% & 0\% & 0\% & 0\% & 13 \\ % 100%
\hline
LuaSocket & 89\% & 1\% & 2\% & 8\% & 123 \\ % 100%
\hline
LuaFileSystem & 89\% & 0\% & 11\% & 0\% & 19 \\ % 100%
\hline
HTTP Digest & 0\% & 0\% & 100\% & 0\% & 1 \\ % 100%
\hline
Typical & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
Modulo 11 & 78\% & 0\% & 0\% & 22\% & 9 \\ % 100%
\hline
Typed Lua Compiler & 93\% & 0\% & 1\% & 6\% & 154 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for each case study}
\label{tab:evalbycase}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
base & 35\% & 4\% & 8\% & 53\% & 26 \\ % 100%
\hline
coroutine & 14\% & 0\% & 0\% & 86\% & 7 \\ % 100%
\hline
package & 62\% & 0\% & 0\% & 38\% & 8 \\ % 100%
\hline
string & 75\% & 0\% & 0\% & 25\% & 16 \\ % 100%
\hline
utf8 & 100\% & 0\% & 0\% & 0\% & 6 \\ % 100%
\hline
table & 14\% & 72\% & 14\% & 0\% & 7 \\ % 100%
\hline
math & 81\% & 0\% & 19\% & 0\% & 27 \\ % 100%
\hline
io & 81\% & 0\% & 0\% & 19\% & 21 \\ % 100%
\hline
os & 82\% & 0\% & 18\% & 0\% & 11 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Lua Standard Library}
\label{tab:evallsl}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
md5 & 100\% & 0\% & 0\% & 0\% & 13 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for MD5}
\label{tab:evalmd5}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
socket & 83\% & 0\% & 0\% & 17\% & 60 \\ % 100%
\hline
ftp & 83\% & 0\% & 17\% & 0\% & 6 \\ % 100%
\hline
http & 80\% & 0\% & 20\% & 0\% & 5 \\ % 100%
\hline
smtp & 100\% & 0\% & 0\% & 0\% & 7 \\ % 100%
\hline
mime & 100\% & 0\% & 0\% & 0\% & 17 \\ % 100%
\hline
ltn12 & 95\% & 5\% & 0\% & 0\% & 20 \\ % 100%
\hline
url & 100\% & 0\% & 0\% & 0\% & 8 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for LuaSocket}
\label{tab:evalsocket}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
lfs & 89\% & 0\% & 11\% & 0\% & 19 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for LuaFileSystem}
\label{tab:evallfs}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
http-digest & 0\% & 0\% & 100\% & 0\% & 1 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for HTTP Digest}
\label{tab:evalhttpdigest}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
typical & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Typical}
\label{tab:evaltypical}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
mod11 & 78\% & 0\% & 0\% & 22\% & 9 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Modulo 11}
\label{tab:evalmod11}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{Total} \\
\hline
tlast & 98\% & 0\% & 2\% & 0\% & 47 \\ % 100%
\hline
tltype & 100\% & 0\% & 0\% & 0\% & 65 \\ % 100%
\hline
tlst & 100\% & 0\% & 0\% & 0\% & 26 \\ % 100%
\hline
tllexer & 18\% & 0\% & 0\% & 82\% & 11 \\ % 100%
\hline
tlparser & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
tldparser & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
tlchecker & 100\% & 0\% & 0\% & 0\% & 2 \\ % 100%
\hline
tlcode & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Typed Lua Compiler}
\label{tab:evaltlc}
\end{table}

>>>>

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Case study} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
Lua Standard Library & 64\% & 5\% & 8\% & 23\% & 129 \\ % 100%
\hline
MD5 & 100\% & 0\% & 0\% & 0\% & 13 \\ % 100%
\hline
LuaSocket & 89\% & 1\% & 2\% & 8\% & 123 \\ % 100%
\hline
LuaFileSystem & 89\% & 0\% & 11\% & 0\% & 19 \\ % 100%
\hline
HTTP Digest & 0\% & 0\% & 100\% & 0\% & 1 \\ % 100%
\hline
Typical & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
Modulo 11 & 78\% & 0\% & 0\% & 22\% & 9 \\ % 100%
\hline
Typed Lua Compiler & 93\% & 0\% & 1\% & 6\% & 154 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for each case study}
\label{tab:evalbycase}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
base & 35\% & 4\% & 8\% & 53\% & 26 \\ % 100%
\hline
coroutine & 14\% & 0\% & 0\% & 86\% & 7 \\ % 100%
\hline
package & 62\% & 0\% & 0\% & 38\% & 8 \\ % 100%
\hline
string & 75\% & 0\% & 0\% & 25\% & 16 \\ % 100%
\hline
utf8 & 100\% & 0\% & 0\% & 0\% & 6 \\ % 100%
\hline
table & 14\% & 72\% & 14\% & 0\% & 7 \\ % 100%
\hline
math & 81\% & 0\% & 19\% & 0\% & 27 \\ % 100%
\hline
io & 81\% & 0\% & 0\% & 19\% & 21 \\ % 100%
\hline
os & 82\% & 0\% & 18\% & 0\% & 11 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Lua Standard Library}
\label{tab:evallsl}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
md5 & 100\% & 0\% & 0\% & 0\% & 13 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for MD5}
\label{tab:evalmd5}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
socket & 83\% & 0\% & 0\% & 17\% & 60 \\ % 100%
\hline
ftp & 83\% & 0\% & 17\% & 0\% & 6 \\ % 100%
\hline
http & 80\% & 0\% & 20\% & 0\% & 5 \\ % 100%
\hline
smtp & 100\% & 0\% & 0\% & 0\% & 7 \\ % 100%
\hline
mime & 100\% & 0\% & 0\% & 0\% & 17 \\ % 100%
\hline
ltn12 & 95\% & 5\% & 0\% & 0\% & 20 \\ % 100%
\hline
url & 100\% & 0\% & 0\% & 0\% & 8 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for LuaSocket}
\label{tab:evalsocket}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
lfs & 89\% & 0\% & 11\% & 0\% & 19 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for LuaFileSystem}
\label{tab:evallfs}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
http-digest & 0\% & 0\% & 100\% & 0\% & 1 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for HTTP Digest}
\label{tab:evalhttpdigest}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
typical & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Typical}
\label{tab:evaltypical}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
mod11 & 78\% & 0\% & 0\% & 22\% & 9 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Modulo 11}
\label{tab:evalmod11}
\end{table}

@@

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c}{} & \multicolumn{4}{|c|}{percentage of members} & \multicolumn{1}{c}{} \\
\hline
\textbf{Module} & \textbf{easy} & \textbf{poly} & \textbf{over} & \textbf{hard} & \textbf{\# members} \\
\hline
tlast & 98\% & 0\% & 2\% & 0\% & 47 \\ % 100%
\hline
tltype & 100\% & 0\% & 0\% & 0\% & 65 \\ % 100%
\hline
tlst & 100\% & 0\% & 0\% & 0\% & 26 \\ % 100%
\hline
tllexer & 18\% & 0\% & 0\% & 82\% & 11 \\ % 100%
\hline
tlparser & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
tldparser & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
tlchecker & 100\% & 0\% & 0\% & 0\% & 2 \\ % 100%
\hline
tlcode & 100\% & 0\% & 0\% & 0\% & 1 \\ % 100%
\hline
\end{tabular}
\end{center}
\caption{Evaluation results for Typed Lua Compiler}
\label{tab:evaltlc}
\end{table}

### 2015-08-13 doc/thesis/review.tex
Improving table formats

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|l|p{6cm}|c|}
\hline
\multirow{5}{*}{table constructor}
& create a record & 36\% \\
\cline{2-3}
& create a list & 29\% \\
\cline{2-3}
& create an empty table & 26\% \\
\cline{2-3}
& create a table with a record part and a list part & 8\% \\
\cline{2-3}
& create a table with non-literal keys & 1\% \\
\hline
\multirow{4}{*}{table access}
& reading with literal keys & 80\% \\
\cline{2-3}
& writing with literal keys & 10\% \\
\cline{2-3}
& reading with non-literal keys & 6\% \\
\cline{2-3}
& writing with non-literal keys & 4\% \\
\hline
\multirow{2}{*}{iteration over tables} &
files that iterate over a list & 27\% \\
\cline{2-3}
& files that iterate over a map & 23\% \\
\hline
\multirow{4}{*}{function declarations}
& inspect the tags of their input parameters & 9\% \\
\cline{2-3}
& return multiple values to signal errors & 6\% \\
\cline{2-3}
& are variadic & 8\% \\
\cline{2-3}
& are method declarations & 23\% \\
\hline
\multirow{1}{*}{object-oriented programming}
& projects that use metatables and declare methods & 45\% \\
\hline
\multirow{2}{*}{modules}
& files that are modules & 61\% \\
\cline{2-3}
& files that are plain scripts & 39\% \\
\hline
\end{tabular}
\end{center}
\caption{Summary of the statistics about the usage of Lua}
\label{tab:statistics}
\end{table}

>>>>

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|p{6cm}|p{6cm}|c|}
\hline
\multirow{5}{*}{\minitab[l]{table constructor \\ (\% per static occurrences)}}
& create a record & 36\% \\
\cline{2-3}
& create a list & 29\% \\
\cline{2-3}
& create an empty table & 26\% \\
\cline{2-3}
& create a table with a record part and a list part & 8\% \\
\cline{2-3}
& create a table with non-literal keys & 1\% \\
\hline
\multirow{4}{*}{\minitab[l]{table access \\ (\% per static occurrences)}}
& reading with literal keys & 80\% \\
\cline{2-3}
& writing with literal keys & 10\% \\
\cline{2-3}
& reading with non-literal keys & 6\% \\
\cline{2-3}
& writing with non-literal keys & 4\% \\
\hline
\multirow{2}{*}{\minitab[l]{iteration over tables \\ (\% per files)}} &
files that iterate over a list & 27\% \\
\cline{2-3}
& files that iterate over a map & 23\% \\
\hline
\multirow{4}{*}{\minitab[l]{function declarations \\ (\% per static occurrences)}}
& inspect the tags of their input parameters & 9\% \\
\cline{2-3}
& return multiple values to signal errors & 6\% \\
\cline{2-3}
& are variadic & 8\% \\
\cline{2-3}
& are method declarations & 23\% \\
\hline
\multirow{1}{*}{\minitab[l]{object-oriented programming \\ (\% per projects)}}
& projects that use metatables and declare methods & 45\% \\
\hline
\multirow{2}{*}{\minitab[l]{modules \\ (\% per files)}}
& files that are modules & 61\% \\
\cline{2-3}
& files that are plain scripts & 39\% \\
\hline
\end{tabular}
\end{center}
\caption{Summary of the statistics about the usage of Lua}
\label{tab:statistics}
\end{table}
